### 2022-10-26 Draft2.Rmd
progress

all_abilities %>% group_by(abilities) %>% summarise(count = n()) %>% 
  arrange(desc(count)) %>% View()

@@

pokemon_copy2
```

@@

>>>>

all_abilities %>% group_by(abilities) %>% summarise(count = n(), capture_rate = mean(capture_rate)) %>% 
  arrange(desc(count)) %>% View()

@@

pokemon_copy2 %>% group_by(abilities) %>%  summarise(count = n(), capture_rate = mean(capture_rate)) %>% 
  arrange(desc(count)) %>% View()
```

@@

```{r}
mean(pokemon_copy2$capture_rate)
```
